---
title: "homework 1"
author: "Zihan Yu"
output:
  github_document: default
  pdf_document: default
---

This is my solution to HW1.

```{r}
library(tidyverse)
```

## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
  )
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

Convert the logical vector to numeric, and multiply the random sample by the result.
Convert the logical vector to a factor, and multiply the random sample by the result.
Convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result.
```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp_gt_0)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp_gt_0)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp_gt_0)
```

## Problem 2

```{r}
install.packages("palmerpenguins")
```

```{r}
data("penguins", package = "palmerpenguins")
```

Variables in penguins are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year. Species, island and sex are factors. Bill_length_mm and bill_depth_mm are numbers. Flipper_length_mm, body_mass_g and year are integers. This dataset has 344 rows and 8 columns. Mean of flipper_length_mm is NA because there are missing values in this column. 

```{r}
penguins
nrow(penguins)
ncol(penguins)
mean(pull(penguins, flipper_length_mm))
```

```{r}
library(ggplot2)
plot = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("plot.png")
```


